\documentclass[sigchi, review]{acmart}

\usepackage{booktabs} % For formal tables

% Copyright
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
% \setcopyright{licensedcagov}
%\setcopyright{cagovmixed}
%\setcopyright{licensedothergov}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[CHI'19]{ACM SigCHI conference}{April 2019}{ElPaso, Texas USA}
\acmYear{2019}
\copyrightyear{2019}

\acmPrice{15.00}
\usepackage{CJKutf8}

\usepackage{multicol}
\usepackage{multirow}
\usepackage{array}
\usepackage{booktabs}
\usepackage[utf8]{inputenc}

\begin{document}
\begin{CJK*}{UTF8}{gbsn}

\title{A Conceptual Framework of Delay Perception in 3D Tele-Immersion}

\titlenote{Produces the permission block, and copyright information}
\subtitle{Extended Abstract}
\subtitlenote{The full version of the author's guide is available as
  \texttt{acmart.pdf} document}

\author{Leave Authors Anonymous}
\affiliation{
  \institution{Institute}
  \city{City}
  \state{Country}
}
\email{example@email.com}

\author{Leave Authors Anonymous}
\affiliation{
  \institution{Institute}
  \city{City}
  \state{Country}
}
\email{example@email.com}

\author{Leave Authors Anonymous}
\affiliation{
  \institution{Institute}
  \city{City}
  \state{Country}
}
\email{example@email.com}

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{B. Trovato et al.}

\begin{abstract}

3D Tele-Immersion (3DTI) allows distributed users to communicate in a same virtual space. It grows rapidly in recent years. However, few works were conducted to study user experience in 3DTI. Delay is an important factor that affects user experience. In this paper, we explore users' perception of network delay in 3DTI. We propose a conceptual framework that levels delay requirements of 3DTI tasks into three classes: \emph{synchronous} tasks, \emph{audiovisual} tasks and \emph{visual Only} tasks. \emph{synchronous} tasks involves interactions at the same time, e.g., instrument ensemble and the Rock-Paper-Scissors game. They require a low delay of 30 $\sim$ 100 ms. We suggest that 3DTI supports much more tasks of this delay-sensitive level compared to the 2D situation. The other two levels are common in 2D, e.g., teleconference and playing chess. We suggest that they require a delay of 200 ms or more in 3DTI. The requirement is lower because the users are less sensitive and more tolerable to delay in 3D. We describe an example study to illustrate our framework. For each level, the framework gives suggestions of network engineering to save network resources and improve the user experience.

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003120.10003121.10003126</concept_id>
<concept_desc>Human-centered computing~HCI theory, concepts and models</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{Human-centered computing~HCI theory, concepts and models}

\keywords{Delay perception; 3D tele-immersion}

\maketitle

\input{sections/introduction.tex}

\input{sections/framework.tex}

\input{sections/system.tex}

\input{sections/experiment.tex}

\input{sections/relatedwork.tex}

\input{sections/limitation.tex}

\section{Conclusion}

This paragraph is for the conclusion.

\begin{acks}

We thank all the volunteers, and all publications support and staff, who wrote and provided helpful comments on previous versions of this document. Authors 1, 2, and 3 gratefully acknowledge the grant from NSF (\#1234--2012--ABC). \textit{This whole paragraph is just an example.}

\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

\end{CJK*}

\end{document}
